Cybersecurity in UK Higher Education?

### 2019-09-15 ITNow_TP_v2.tex
Attempt to change audience

% authors
\author[1]{Tom Crick}
\author[2]{James H. Davenport}
\author[3]{Alastair Irons}
\author[4]{Tom Prickett}
% institutions
\affil[1]{Swansea University, Swansea, UK}
\affil[2]{University of Bath, Bath, UK}
\affil[3]{Sunderland University, Sunderland, UK}
\affil[4]{Northumbria University, Newcastle upon Tyne, UK}
% emails
\affil[1]{\url{thomas.crick@swansea.ac.uk}}
\affil[2]{\url{j.h.davenport@bath.ac.uk}}
\affil[3]{\url{alastair.irons@sunderland.ac.uk}}
\affil[4]{\url{tom.prickett@northumbria.ac.uk}}

@@

\date{August 2019}

@@

\begin{strapline}
The BCS has been promoting further inclusion of Cybersecurity within general Computer Science University Education since 2010. We explore progress and some of the outstanding related issues.

\end{strapline}

@@

Cybersecurity matters! Breaches are legion and sadly are a common feature in the news. Universities are  addressing the demand for educated cybersecurity professionals.  There are calls for formal education to respond to this situation. This is reinforced by a wider focus on digital skills and computer science education reform, especially across the nations of the UK.

This raises the question, should cybersecurity be of importance for all or just for specialists? There is a serious need for cybersecurity specialists, but also all in IT need to know \emph{some} cybersecurity -- thus, there is a case for both.

In this article we explore some of the challenges related to cybersecurity education of general computer scientists (including information technology and other related degrees), and what we, the BCS, have been doing to enhance cybersecurity in education at university.

@@

\section*{Challenges} \label{sec}
% TC: pick a couple of these as examples?
\subsection*{Educational Resources}\label{sec:EDResource}
It is hard to determine what is actually delivered as part of a degree programme, but a reasonable proxy for this are recommended textbooks and other supporting resources.
\subsubsection*{The Case of SQL Injection}\label{sec:SQL}
SQL injection is a major weakness: number one in the Open Web Application Security Project (OWASP) Top 10, and has been in the Top 10 since at least 2003. Database textbooks were analysed in 2019 ~\cite{Drop2019}.  There were seven such books, but three books accounted for the 36 of 44 universities. Five of the seven (30 of the 44) had no mention of SQL injection. On the other two, the more popular one has a seriously flawed discussion.

\subsubsection*{The Case of Java}\label{sec:Java}

Many Java books do not cover security.  If you want to know about security you need to look at the documentation of the package/API being used, and/or  informal resources. \cite{Mengetal2018a} analysed 503 cybersecurity-related postings on the popular Stack Overflow online resource. 53\% were about the Spring Security framework, dominated by authentication (45\%). One example being, by default, Spring enables protection against cross-site request forgery (CSRF). But all the accepted answers to CSRF-related failures simply suggested disabling the check. There were no negative comments about this, and indeed a typical response is ``{\emph{Adding}} \verb!csrf().disable()!
{\emph{{solved the issue!!! I have no idea why it was enabled by default}}''. }

\subsubsection*{Android}\label{sec:Android}

For Android, \cite{Fischeretal2017a} looked specifically at the use of resources from Stack Overflow. The key finding was:

\begin{quote}
``{\emph{We found that 15.4\% of all 1.3 million Android applications
contained security-related code snippets from
Stack Overflow. Out of these 97.9\% contain at least one
insecure code snippet.}}''
\end{quote}

\subsubsection*{Informal Resources}\label{sec:informal}

The web abounds with informal resources, such as tutorials and code snippets. How good are these? One investigation \cite{Unruhetal2017a}, took the top five search results from Google for six queries. Of these 30 tutorials, six had SQL injection weaknesses, and three had Cross-Site Scripting (Number 7 in OWASP's Top Ten) weaknesses. Searching for these fragments in PHP projects on GitHub found 820 instances of these fragments, of which 117 were verified manually to be vulnerable --- 80\% of which were vulnerable to SQL injection.

\subsection*{Who will teach the Cybersecurity?}\label{sec:staffing}

Cybersecurity skills are in short supply, in both industry and academia. The demand for cybersecurity skills in industry makes it difficult for academia to attract academics with knowledge, practical experience, research background and academic aspirations. As universities expand their cybersecurity provision it is not uncommon to find multiple jobs advertised at the same time.

@@

 The BCS has been using the accreditation process to mandate formal inclusion of information security (2010) and then cybersecurity (2013) within the programmes we accredit.

@@

>>>>

% authors
\author[1]{Tom Crick}
\author[2]{James H. Davenport}
\author[3]{Alastair Irons}
\author[4]{Sally Pearce}
\author[5]{Tom Prickett}
% institutions
\affil[1]{Swansea University, Swansea, UK}
\affil[2]{University of Bath, Bath, UK}
\affil[3]{Sunderland University, Sunderland, UK}
\affil[4]{Accreditation Team Manager,BCS}
\affil[5]{Northumbria University, Newcastle upon Tyne, UK}
% emails
\affil[1]{\url{thomas.crick@swansea.ac.uk}}
\affil[2]{\url{j.h.davenport@bath.ac.uk}}
\affil[3]{\url{alastair.irons@sunderland.ac.uk}}
\affil[3]{\url{sally.pearce@BCS.uk}}
\affil[5]{\url{tom.prickett@northumbria.ac.uk}}

@@

\date{September 2019}

@@

\begin{strapline}
"Every Computer Science Degree Should Require a Course in Cybersecurity". We explore the progress to date.
\end{strapline}

@@

On the 27th August of this year the Harvard Business Review reported "Every Computer Science Degree Should Require a Course in Cybersecurity". How could you argue with the intent of this suggestion? The BCS has been promoting this for a number of years and how fantastic to see our concerns highlighted to such an audience. But, and this is a subtly but significant \textit{'but'}, is this the best approach? We feel not. As our recent research {\cite{Cricketal2019}} has argued cybersecurity is too important to be left to specialists and needs to be everyone's responsibility and addressed across a course.

This article explores some challenges regarding how cybersecurity is taught which informs this view and provides a progress report regarding BCS efforts to promote the inclusion of cybersecurity in degree course.

@@

\section*{Challenges} \label{sec}
% TC: pick a couple of these as examples?
\subsection*{Educational Resources}\label{sec:EDResource}
%It is hard to determine what is actually delivered as part of a degree programme, but a reasonable proxy for this are recommended textbooks and other supporting resources.
Lets start by looking at the books and other resources that are used to teach degrees. Do these support the promotion of good cybersecurity practices? As you will see, a single course on the subject may not be enough. We think that would be like \textit{'shutting the proverbial stable door after the horse has bolted'}. 
\subsubsection*{Databases}\label{sec:SQL}
A core part of any computer science degree. SQL injection is a major weakness: number one in the Open Web Application Security Project (OWASP) Top 10, and has been in the Top 10 since at least 2003. Database textbooks were analysed in 2019 ~\cite{Drop2019}.  This work shows this flaw is not being addressed. Small wonder it continues to be an issue!

\subsubsection*{The Case of Java}\label{sec:Java}
Our research shows Java is still the most commonly taught programme language at universities in the UK. Many Java books do not cover security.  If you want to know about security you need to look at the documentation of the package/API being used, and/or  informal resources. \cite{Mengetal2018a} analysed this and Stack Overflow in particular. Looking at the Spring Framework 53\% of questions related to cybersecurity were dominated by authentication (45\%). One example being, by default, Spring enables protection against cross-site request forgery (CSRF). But all the accepted answers to CSRF-related failures simply suggested disabling the check. There were no negative comments about this, and indeed a typical response is ``{\emph{Adding}} \verb!csrf().disable()!
{\emph{{solved the issue!!! I have no idea why it was enabled by default}}''. } Quite concerning!

\subsubsection*{Informal Resources}\label{sec:informal}
The web abounds with informal resources, such as tutorials and code snippets. How good are these? One investigation \cite{Unruhetal2017a} considered 30 popular tutorials and found six had SQL injection weaknesses, and three had Cross-Site Scripting (Number 7 in OWASP's Top Ten) weaknesses. Looking for related code fragments on GitHub, found 820 instances of these fragments, of which 117 were verified manually to be vulnerable --- 80\% of which were vulnerable to SQL injection. Hardly encouraging.

%took the top five search results from Google for six queries. Of these 30 tutorials, six had SQL injection weaknesses, and three had Cross-Site Scripting (Number 7 in OWASP's Top Ten) weaknesses. Searching for these fragments in PHP projects on GitHub found 820 instances of these fragments, of which 117 were verified manually to be vulnerable --- 80\% of which were vulnerable to SQL injection.

\subsection*{Who will teach the Cybersecurity?}\label{sec:staffing}
Enough about the books, who is going to teach this? Cybersecurity skills are in short supply, in both industry and academia. The demand for cybersecurity skills in industry makes it difficult for academia to attract academics with knowledge, practical experience, research background and academic aspirations. As universities expand their cybersecurity provision it is not uncommon to find multiple jobs advertised at the same time.

@@

Enough of the challenges. What have we been doing about it? The BCS has been using the accreditation process to mandate formal inclusion of information security (2010) and then cybersecurity (2013) within the programmes we accredit.

@@

Is it sufficient to leave to cybersecurity to Computer Scientist? We hope this is conversation that will begin shortly.
